---
title: "Introduction to spatialRegroup"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to spatialRegroup}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

The `spatialRegroup` package identifies spatial units that are
statistically more similar to a neighboring group than to their own.
It is particularly useful for detecting boundary effects between
administrative units such as EPCI, districts, or counties.

## Installation

```{r install, eval=FALSE}
devtools::install_github("ause31/-Spatial-Regrouping-by-Attributive-Affinity")
```

## Basic example

```{r example}
library(sf)
library(dplyr)
library(spatialRegroup)

# Create a simulated 4x4 grid
set.seed(123)
grid <- st_make_grid(
  st_as_sfc(st_bbox(c(xmin=0, ymin=0, xmax=100, ymax=100))),
  n = c(4, 4)
)

polygons <- st_as_sf(data.frame(geometry = grid)) %>%
  mutate(
    id   = row_number(),
    EPCI = paste0("G", ceiling(id / 4)),
    rev  = rnorm(16, 30000, 5000),
    prix = rnorm(16, 3000,  500)
  )

# Run spatialRegroup
result <- spatialRegroup(
  data      = polygons,
  group_var = "EPCI",
  vars_attr = c("rev", "prix"),
  verbose   = TRUE
)

# Results
table(result$candidate)
```

## Interpreting results

The output contains two key columns:

- `candidate` : TRUE if the unit was reclassified
- `EPCI_regroup` : the new group after reclassification

## Comparing partitions with multilevel models

```{r models, eval=FALSE}
library(lme4)
library(performance)

m_init <- lmer(rev ~ prix + (1|EPCI),        data = result, REML = FALSE)
m_new  <- lmer(rev ~ prix + (1|EPCI_regroup), data = result, REML = FALSE)

data.frame(
  modele = c("Initial", "Recomposed"),
  AIC    = round(c(AIC(m_init), AIC(m_new)), 1)
)
```
